Summary Tables

### 2019-05-09 summary_tables.Rmd
Add case study specific propensities - as outputted from multi-city script

```{r load_objects = "asis"}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
cities <- c('accra','sao_paulo','delhi','bangalore')

@@

>>>>

```{r load_objects = "asis"}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
cities <- c('accra','sao_paulo','delhi','bangalore')
# cities <- c('sao_paulo')

@@

## Case study specific propensities

|accra|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 96.7|66.2|2.0 |
| bicycle | 0.6|0.3|0.4 |
| car | 1.0|10.4|16.9 |
| motorcycle | 0.2|0.9|2.7 |
| bus | 0.0|18.6|69.4 |

|sao_paulo|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 65.4|6.9|2.9 |
| bicycle | 0.7|0.9|0.3 |
| car | 22.2|41.9|27.2 |
| motorcycle | 1.3|2.7|3.5 |
| bus | 9.7|43.0|35.8 |

|delhi|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 83.5|28.8|1.8 |
| bicycle | 2.0|5.8|4.7 |
| car | 2.0|10.7|16.8 |
| motorcycle | 5.6|23.3|20.7 |
| bus | 1.2|18.2|39.1 |

|bangalore|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 89.7|28.6|1.2 |
| bicycle | 2.6|10.9|0.9 |
| car | 0.8|5.0|4.9 |
| motorcycle | 4.8|37.3|48.2 |
| bus | 0.6|8.3|29.3 |
